% TEMPLATE for Usenix papers, specifically to meet requirements of
%  USENIX '05
% originally a template for producing IEEE-format articles using LaTeX.
%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
% adapted by David Beazley for his excellent SWIG paper in Proceedings,
%   Tcl 96
% turned into a smartass generic template by De Clarke, with thanks to
%   both the above pioneers
% use at your own risk.  Complaints to /dev/null.
% make it two column with no page numbering, default is 10 point

% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
% the .sty file from the LaTeX source template, so that people can
% more easily include the .sty file into an existing document.  Also
% changed to more closely follow the style guidelines as represented
% by the Word sample file. 

% Note that since 2010, USENIX does not require endnotes. If you want
% foot of page notes, don't include the endnotes package in the 
% usepackage command, below.


\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{xcolor}


\renewcommand{\enoteheading}{%
  \section*{Notes}
  \vspace{-0.5em}
}

\definecolor{termcmd}{RGB}{0,80,180}
\definecolor{termbg}{RGB}{248,248,248}
\definecolor{termerr}{RGB}{160,30,30}
\definecolor{termok}{RGB}{20,110,40}
\definecolor{termgray}{RGB}{90,90,90}

\lstdefinestyle{terminal}{
basicstyle=\ttfamily\scriptsize,
breaklines=true,
frame=tb,
framerule=0.4pt,
rulecolor=\color{gray!50},
backgroundcolor=\color{termbg},
xleftmargin=6pt,
xrightmargin=6pt,
columns=flexible,
keepspaces=true,
showstringspaces=false,
aboveskip=3pt,
belowskip=3pt,
moredelim=[il][\color{termcmd}\bfseries]{\$ },
moredelim=[il][\color{termerr}\bfseries]{ERROR},
moredelim=[il][\color{termok}]{[+]},
moredelim=[il][\color{termgray}]{[*]},
}


\begin{document}
%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf CS-412 Lab 2: Fuzzing Lib-PNG }

\author{
{\rm Wajiha Masood}\\
\and
{\rm Nicolas Sozzi}\\
\and
{\rm Sara Bosi}\\
\and
{\rm Adrian Martinez}
}

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}

\section*{Introduction}
Fuzzing is a widely used technique for discovering vulnerabilities in software by automatically generating and mutating inputs to trigger unexpected behavior. In this lab, we apply coverage-guided fuzzing to libpng 1.4.8, a widely deployed open-source library for decoding and encoding PNG images, using AFL++. Given that libpng is embedded in browsers, image editors, and countless other applications, memory corruption bugs in its parsing logic can have significant real-world impact. We describe the design of our fuzzing harness, our instrumentation choices, seed corpus construction, and the analysis of crashes discovered during the campaign, including a heap-based out-of-bounds read in the iTXt chunk parser.

\section {Harness Design}
We selected \texttt{png\_read\_info()}, \texttt{png\_read\_image()} along with the progressive parser using the
\texttt{png\_process\_data()} API as the main entries in the harness. Such APIs make great targets for fuzzing since they are responsible for parsing the user-supplied PNG file and involve complicated operations like handling the chunks in the image, parsing, decompressing the image contents, transforming color values and allocating memory dynamically. The decoders are traditionally one of the main culprits when it comes to memory corruption bugs since the binary format could easily cause an out-of-bounds access, integer overflows or heap corruption.
\subsection{Alternative Entry Points}
We also explored Libpng write/encoder APIs such as \texttt{png\_write\_image()} and other write APIs,  but fuzzing the decoder API was found to be more promising as decoding involves working with user-generated PNG files, whereas encoding works with image data generated by applications. Fuzzing the decoder revealed much more interesting behavior than fuzzing the write API; no crashes were encountered when fuzzing the latter. Thus, the decoder APIs were chosen as the main target for fuzzing.
\subsection{Harness Data flow}
The workflow for the harness starts with AFL++ generating a mutated PNG input and passing it to the harness. The input file is then read into a memory buffer that is modeled as a struct that contains data pointers to the input, total size and current offset. With a customized callback function passed to \texttt{png\_set\_read\_fn()}, libpng will be able to read directly from the AFL++ controlled buffer instead of from a regular file stream. Through repeated callbacks during execution, libpng will keep requesting bytes, which results in the AFL++ mutated input being sent to the parser. The typical harness involves initializing structures in libpng, reading the PNG header information with \texttt{png\_read\_info()}, reading metadata from the header using \texttt{png\_get\_IHDR()}, activating multiple transform functions, allocating buffers for rows, decoding the PNG images with \texttt{png\_read\_image()}, and lastly parsing additional chunks with \texttt{png\_read\_end()}.

\subsection{Guard Rationale}

Several guards were included to increase fuzzing robustness and ensure that all crashes occur only because of libpng code rather than harness itself. Checks for null after function calls \texttt{png\_create\_read\_struct()} and \texttt{png\_create\_info\_struct()} ensure that crashes are not occurring trivially due to failed allocations. It's crucial to include the \texttt {setjmp(png\_jmpbuf(png))} check because of longjmp based error handling implemented by libpng internally when an invalid PNG file is encountered. Without this mechanism, one bad input can stop fuzzing altogether. Bounds checking inside the custom read function ensures that there will not be any potential out-of-bound reads from the input buffer provided by AFL++. Setting dimensions limits through \texttt{png\_set\_user\_limits()} allows for preventing AFL++ from generating huge PNG images with potentially high memory consumption or denial-of-service attacks. Finally, proper checking and cleanup are specially important in persistent mode since otherwise, memory leaks will be accumulated between successive fuzz runs.

\section {Instrumentation and Sanitizers}
\begin{itemize}[leftmargin=*,noitemsep,topsep=2pt]
    \item \textbf{AFL++ Instrumentation (\texttt{afl-clang-fast}):}
The target (libpng 1.4.8) was compiled using AFL++ instrumentation with afl-clang-fast compiler flags. This is done in order to instrument the executable so AFL++ can detect execution of any new code path during fuzzing. Without it, AFL++ would mutate inputs mostly blindly and path discovery would be much weaker.
\item \textbf{AddressSanitizer (ASan):}
Address Sanitizer was also used for detecting memory-related bugs such as buffer overflow, out-of-bound access or use after free errors when performing crash analysis to reproduce the bug. In absence of Address Sanitizer, some memory problems can fail to produce a crashable bug or become difficult to debug.
\item \textbf{Persistent Mode (\texttt{\_\_AFL\_LOOP()}):}
For the persistent-mode campaign, the harness used  AFL++’s \texttt{\_AFL\_LOOP()} mechanism. This removes the need to restart the program after every test input, increasing the number of executions per second. The absence of this function will not affect correctness but will slow down the fuzzing process.
 \item \textbf{CRC-32 Patch:}
A libpng CRC-32 checksum patch was applied from AFL++’s libpng no-checksum utility. Normally, random input mutations leads to corruption of PNG chunk CRCs and results in file rejection by libpng before parsing takes place. The disabling of CRC checking increases the efficiency of coverage as mutated chunks can bypass this part of code and proceed to other parts.
 \item \textbf{PNG Dictionary and Corpus Minimization:}
Finally, PNG dictionary and corpus minimization are used to create a small seed pool that will enable AFL++ to produce PNG files correctly. It is important for efficiency purposes, although absence of these does not hinder the fuzzing process itself.
\end{itemize}

\input{sections/q3}
\input{sections/q4}
\input{sections/q5}
\input{sections/q6}
\input{sections/q7}
\input{sections/q8}

{\footnotesize \bibliographystyle{acm}
\bibliography{sample}}

\theendnotes

\clearpage
\onecolumn
\appendix
\renewcommand{\thefigure}{\thesection.\arabic{figure}}

\input{appendices/campaign_results_appendix}
\input{appendices/q7_appendix}

\end{document}







